The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex
add result at section4

The results of our target project are as follows table1
\begin{table} [H]
  \caption{Number of requirements}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    &ECLIPSE PLATFORM&FIREFOX BROWSER\\
    \midrule
    Reported in 2017& 1 & 1 \\
    Resolved in 2018 & 1&1 \\
    \bottomrule
  \end{tabular}
\label{table:Dataset}
\end{table}

@@

\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplotraw.png}
    \caption{Priority-number of comments}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplot.png}
    \caption{Priority-Log(number of comments)}
  \end{subfigure}
  \caption{The same cup of coffee. Two times.}
  \label{fig:priority_comments}
\end{figure*}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ec.png}
    \caption{Eclipse}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ff.png}
    \caption{Firefox}
  \end{subfigure}
  \caption{Average Time cost at 2016 and 2017 per components}
  \label{fig:time_cost}
\end{figure*}
\subsection{Profit}

@@

Cost: Average resolution time for the requirements of the same component as the previous year

@@

\subsection{Result}

\begin{table} [H]
  \caption{Dataset from Bugzilla}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    &ECLIPSE&FIREFOX-I&FIREFOX-II&FIREFOX-III\\
    \midrule
    Cost& 50699.70& 262945.50& 262945.50& 262945.50 \\
    Profit& 3489.64& 13025.88& 12210& 26332.88 \\
    \bottomrule
  \end{tabular}
\label{table:Dataset}
\end{table}

>>>>

The results of our target project are as follows table1
\begin{table} [H]
  \caption{Number of requirements}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    &ECLIPSE PLATFORM&FIREFOX BROWSER\\
    \midrule
    Reported in 2017& 2053 & 5593 \\
    Resolved in 2018 & 817 & 2938 \\
    \bottomrule
  \end{tabular}
\label{table:Dataset}
\end{table}

@@

\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplotraw.png}
    \caption{Priority-number of comments}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplot.png}
    \caption{Priority-Log(number of comments)}
  \end{subfigure}
  \caption{The relation ship between Priority and Number of Comments}
  \label{fig:priority_comments}
\end{figure*}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ec.png}
    \caption{Eclipse}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ff.png}
    \caption{Firefox}
  \end{subfigure}
  \caption{Average Time cost at 2016 and 2017 per components}
  \label{fig:time_cost}
\end{figure*}
\subsection{Profit}

@@

\textbf{Cost}: \textit{Average resolution time for the requirements of the same component as the previous year}

@@

 To illustrate this, we compared the average time cost in 2016 to the average time cost in 2017. Figure 2 describes this.

As Figure 2.(a) shows, the first, the result in Eclipse repository is quite accurate. The average bug resolution time was similar than we expected. Some exceptions have been found to exist, but more than 60 percent of the components actually match.

But for Figure 2.(b) the result in Firefox repository, we can also see that the order of each component, including absolute time-consuming values, is not quite correct. In Firefox, it was updated almost 200 times a year. Therefore, in 2016 and 2017, the code was not maintained the same, so it make that the actual cost are not constant among the years.

\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}

We have concluded that it is possible to use the past Cost only for projects where updates are infrequent, i.e. projects with some constant structure. This estimate process has many limitations to be used in real industry. It's a very change-sensitive indicator, and it has the potential to be wrong at any time. However, in order to estimate this more accurately, it would be the only way for the developer or project manager to specify the actual estimated time cost. In the absence of such direct data, our estimates will be meaningful.

\subsection{Result}
In conclusion, we were able to create 4 data sets.
\begin{table} [H]
  \caption{Dataset from Bugzilla}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    Repository&Profit definition&True Cost&True Profit\\
    % &ECLIPSE&FIREFOX-I&FIREFOX-II&FIREFOX-III\\
    \midrule
    ECLIPSE-I&Log(comments)&50699.70& 3489.64 \\
    FIREFOX-I&Log(comments)& 262945.50& 13025.8 \\
    FIREFOX-II&Priority& 262945.50& 12210 \\
    FIREFOX-III&Priority+Log(comments)& 262945.50& 26332.88 \\
    \bottomrule
  \end{tabular}
\label{table:Dataset}
\end{table}

In Firefox, the profit was able to use both Priority and Number of Comments, creating a total of three data sets, including each case and the sum of the two indicators. The table also shows the true value of cost & profit that was resolved in 2018. We're going to use this dataset to compare the results of the actual search-based algorithms in the next section.
